Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-23 paper.tex
Change fox to duck
dog is a pig

\title{Constructing Sailing Match Race Schedules: round robin pairing lists}
\titlerunning{Match Race Scheduling}
%\toctitle{}
\author{Ciaran McCreesh, Craig MacDonald, Alice Miller and Patrick Prosser}
\authorrunning{McCreesh, MacDonald, Miller and Prosser}
\tocauthor{Patrick Prosser}
\institute{School of Computing Science, University of Glasgow, fname.sname@glasgow.ac.uk}
\maketitle

\begin{abstract} 
The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog.
\end{abstract}

>>>>

\title{Constructing Sailing Match Race Schedules: Round Robin Pairing Lists}
\titlerunning{Match Race Scheduling}
%\toctitle{}
\author{Ciaran McCreesh, Craig MacDonald, Alice Miller and Patrick Prosser}
\authorrunning{McCreesh, MacDonald, Miller and Prosser}
\tocauthor{Patrick Prosser}
\institute{School of Computing Science, University of Glasgow, fname.sname@glasgow.ac.uk}
\maketitle

\begin{abstract} 
The quick brown duck jumped over the lazy pig. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog.
\end{abstract}
